\documentclass[a4paper]{article}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{charter} % tipografia
% \usepackage{graphicx}
\usepackage{bytefield}
\usepackage[pdftex]{graphicx}
\usepackage{bm} % bold font in math mode
\usepackage{sidecap}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makeidx}
\usepackage{float}
\usepackage{amsmath, amsthm, amssymb}
\newtheorem{theorem}{Teorema}
\newtheorem{customthm}{Teorema}
\newtheorem{corollary}{Corolario}[theorem]
\newtheorem{proposition}[theorem]{Proposición}
\newtheorem{innercustomlemma}{Lemma}
\newenvironment{customlemma}[1]
  {\renewcommand\theinnercustomlemma{#1}\innercustomlemma}
  {\endinnercustomlemma}
\usepackage{amsfonts}
\usepackage{sectsty}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{hyperref} % links
\usepackage{algorithm} %http://www.ctan.org/pkg/algorithms
\usepackage{algorithmic}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\usepackage{tabularx} % tablas copadas
% custom
\input{codesnippet}
\input{page.layout}
\input{extras}
% \setcounter{secnumdepth}{2}
\usepackage{underscore}
\usepackage{kbordermatrix}% Matrix column labels
%\usetikzlibrary{arrows,shapes}
%\usepackage{tkz-graph}
\usepackage{caratula}
\usepackage{url}
\lstset{
    language=C++,
    basicstyle=\ttfamily,
    keywordstyle=\color{blue}\ttfamily,
    stringstyle=\color{red}\ttfamily,
    commentstyle=\color{ForestGreen}\ttfamily,
    morecomment=[l][\color{magenta}]{\#},
    literate={á}{{\'a}}1 {ó}{{\'o}}1 {é}{{\'e}}1 {í}{{\'i}}1 {ú}{{\'u}}1 {Á}{{\'A}}1 {Í}{{\'I}}1 {É}{{\'E}}1 {Ú}{{\'U}}1 {Ó}{{\'O}}1 {\ \ }{{\ }}1,
	breaklines=true,
	tabsize=2
}

\DeclareUnicodeCharacter{2212}{-}

% *********************** %
\usepackage{tikz}
\usetikzlibrary{graphs}
\usetikzlibrary{calc}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
% Otros
\usepackage{arrayjobx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{etoolbox}
\usepackage{listingsutf8}
\lstset{inputencoding=utf8/latin1}
\usepackage{fancyvrb}
\usepackage{float}
\usepackage{abstract}
\newcommand{\subscript}[2]{$#1 _ #2$}


% ******************************************************** %
\begin{document}
\thispagestyle{empty}
\materia{Métodos Numéricos}
\submateria{Segundo Cuatrimestre de 2015}
\titulo{Trabajo Práctico III}
%\subtitulo{Grupo: }
\integrante{Iv\'an Arcuschin}{678/13}{iarcuschin@gmail.com}
\integrante{Mart\'in Jedwabny}{885/13}{martiniedva@gmail.com}
\integrante{Jos\'e Massigoge}{954/12}{jmmassigoge@gmail.com}
\integrante{Iv\'an Pondal}{078/14}{ivan.pondal@gmail.com}
\maketitle
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
   Fact: baby's videos are funny. And they are even funnier when watched in \textit{slow motion}.

   In this work, we look at 4 different Interpolation methods to automatically generate
   \textit{slow motion} videos. This is achieved by interpolating some amount of new frames
   between each pair of original frames. Depending on the method, this procedure
   generates different levels of \textit{smoothness}.

   Once the methods are explained and implementation details are cleared out, we
   will present several experiments, namely in two categories. The first ones, will
   asure that the methods actually work, in the general case of function interpolation.
   The second ones, will provide different ways to compare the quality of the videos
   produced by each method.
\end{abstract}
\vspace{3em}
\renewcommand{\abstractname}{Resumen}
\begin{abstract}
   Hecho: los videos de bebes son graciosos. Y son mucho más gracios cuando se miran en
   \textit{slow motion}.

   En este trabajo, nos centraremos en 4 diferentes métodos de Interpolación para generar
   automaticamente videos en cámara lenta. Esto se logra interpolando una cierta
   cantidad de cuadros nuevos entre cada par de cuadros originales. Dependiendo del
   método, este procedimiento genera diferentes niveles de calidad.

   Una vez que hayamos explicado los métodos junto con su implementación, presentaremos
   varios experimentos, dentro de dos categorías. La primera, asegurará que los métodos
   funcionen correctamente, en el caso general de interpolación de funciones. La
   segunda, proveerá diferentes formas de comparar la calidad de los videos producidos
   por cada método.
\end{abstract}
\vspace{3em}
\textbf{Keywords:} Video, slow motion, interpolation methods, splines
% no footer on the first page
\thispagestyle{empty}
\newpage

\tableofcontents

\newpage
\section{Introducción}
\input{intro}

\newpage
\section{Modelo}
\input{modelo}

\newpage
\section{Implementación}\label{Implementacion}
\input{implementacion}

\newpage
\section{Experimentación}
\input{experimentacion}

\newpage
\section{Conclusión}
\input{conclusion}

\newpage
\bibliographystyle{plain}
\section{Referencias}
\begingroup
\renewcommand{\section}[2]{}
\bibliography{informe}
\endgroup

\newpage
\section{Enunciado}
\input{tp3}

\newpage
\appendix
\input{apendice}

\end{document}
